Software Citation Principles

### 2016-05-09 sc-principles/software-citation-principles.tex
adding a word in 5.4 and adding line breaks

Adherence to the software citation principles enables better peer reviews through improved reproducibility. However, since the primary goal of software citation is to identify the software that has been used in a scholarly product, the peer review of software is mostly out of scope in the context of software citation principles. For instance, when identifying a particular software artifact that has been used in a scholarly product, whether or not that software has been peer-reviewed is irrelevant. One possible exception would be if the peer-review status of the software should
be part of the metadata, but the working group does not believe this to be part of the
minimal metadata needed to identify the software.

>>>>

Adherence to the software citation principles enables better peer reviews through improved
reproducibility. However, since the primary goal of software citation is to identify the
software that has been used in a scholarly product, the peer review of software itself is
mostly out of scope in the context of software citation principles. For instance, when
identifying a particular software artifact that has been used in a scholarly product,
whether or not that software has been peer-reviewed is irrelevant. One possible exception
would be if the peer-review status of the software should
be part of the metadata, but the working group does not believe this to be part of the
minimal metadata needed to identify the software.
